gij bent 2

### 2025-10-01 paper/paper.qmd
Make sure caption appears for influence figure
Voeg TODO toe aan conclusie

```{r #fig-influence}
#| label: fig-influence-boxplot
#| caption: The distribution of the influence metric in our dataset. The bulk of our tweet authors are followed more than they follow others themselves.

@@

>>>>

```{r #fig-influence}
#| label: fig-influence-boxplot
#| fig-cap: The distribution of the influence metric in our dataset. The bulk of our tweet authors are followed more than they follow others themselves.

@@

[[ de discussie mag best wat uitgebreider - nu wat te summier ]]
